\documentclass{scrartcl}	% classe article di KOMA
%http://www.cv-templates.info/2009/10/classicthesis-currvita-latex-cv-template/
\reversemarginpar
\newcommand{\MarginDate}[1]{\marginpar{\raggedleft\itshape\small#1}}
%\usepackage[latin1]{inputenc}	% la codifica di input
%\usepackage[T1]{fontenc}	% la codifica dei font
\usepackage[LabelsAligned]{currvita}	% un buon pacchetto per CV
\usepackage[nochapters]{classicthesis} % stile ClassicThesis
\usepackage{url}	% per gli indirizzi Internet
\usepackage[utf8]{inputenc}
\renewcommand{\cvheadingfont}{\LARGE\color{Blue}}
\renewcommand{\cvlistheadingfont}{\large}
\renewcommand{\cvlabelfont}{\qquad}
%Setup hyperref package, and colours for links, text and headings
\usepackage{hyperref}		
\hypersetup{	colorlinks,breaklinks,
			urlcolor=Blue, 
			linkcolor=Blue}
\usepackage{eurosym}
\newlength{\datebox}\settowidth{\datebox}{Summer 2007}

\newcommand{\NewWorkExperience}[3]{\noindent\hangindent=2em\hangafter=0 \parbox{\datebox}{\textit{#1}}\hspace{1.5em} #2 #3%
\vspace{0.5em}}

\newcommand{\Description}[1]{\hangindent=2em\hangafter=0\noindent\raggedright\footnotesize{#1}\par\normalsize}
\newcommand{\Sep}{\vspace{2em}}
\begin{document}
\thispagestyle{empty}
\begin{cv}{\spacedallcaps{Carlos A. Guerrero M.}}

\spacedlowsmallcaps{Personal Data}

\NewWorkExperience{born}{25 October 1984}{$\cdotp$ San Cristóbal, Venezuela}

\NewWorkExperience{address}{Calle Mariners 12, Piso 5}{$\cdotp$ Barcelona, España}

\NewWorkExperience{email}{\href{mailto:contact@carlosguerrero.com}{contact@carlosguerrero.com}}{$\cdotp$ \href{mailto:guerrerocarlos@gmail.com}{guerrerocarlos@gmail.com}}

\NewWorkExperience{skype}{gnuwarrior}{}

\NewWorkExperience{info}{\href{http://www.carlosguerrero.com}{www.carlosguerrero.com}}{}

\NewWorkExperience{github}{\href{http://github.com/guerrerocarlos}{github.com/guerrerocarlos}}{}

\NewWorkExperience{phone}{+34 627 16 96 69}{}


\noindent\spacedlowsmallcaps{Work Experience}
\vspace{0.5em}



\NewWorkExperience{dec.2011--currently}{\textbf{\href{http://proxydns.co/}{ProxyDNS}} }{}

\Description{\MarginDate{SysAdmin, Security Specialist, Javascript, HTML5, CSS3, Django, Python, Technical Support}Backend development using several VPS and AWS, high performance implementation, security supervision, online automated payment mechanism developed in \textit{Django}, \textit{bind}, \textit{nginx}, \textit{iptables}. Paypal integration. All done from ground up, including marketing, social networks management.}
\Sep

\NewWorkExperience{jan.2013--may.2013}{\textbf{Caracas 360 $\cdotp$ Android App} }{}

\Description{\MarginDate{Android Development}Tourism promoting app, using GPS, augmented reality and QR codes. Can be seen at: \href{https://play.google.com/store/apps/details?id=com.carlosguerrero.caracas360}{https://play.google.com/store/apps/details?id=com.carlosguerrero.caracas360}}
\Sep

\NewWorkExperience{jul.2012--december.2013}{\textbf{Covetel} $\cdotp$}{Venezuela.}

\Description{\MarginDate{
Python|OpenERP Developer and Instructor}\href{http://openerp.com/}{OpenERP} module and drivers development, OpenERP Point of Sale and Fiscal Printers experience. Python, Plone, OpenERP Technical and Funcional Instructor.}
\Sep

\NewWorkExperience{oct.2011--jul.2012}{\textbf{Brightcomms} $\cdotp$}{El Salvador.}

\Description{IT and Development department leader, for all company software development circle and \textbf{talent recruiter}. \MarginDate{IT/DevOp}
Development manager for all local and overseas developers using agile development techniques. Implementation of open source software solutions for enterprise use. Solution Architect for internal software developments. IT monitoring and Security.}
\Sep

\NewWorkExperience{jul.2011--oct.2011}{\textbf{Brightcomms} $\cdotp$}{Nicaragua.}

\Description{Telecom services provider logs extraction from Sybase \MarginDate{Python \& Django Development}
to external Postgresdb with subsecuent processing, analysis and visualization on different types of tables/graphs, reports generated in HTML and PDF, with web and email visualization. Simple web administration interface with KPI creation manager (SQL), and custom reports creation. Due to high volume of data, many optimization methods where implemented. (Django, Sybase, Javascript).}
\Sep

\NewWorkExperience{2008--2011}{\textbf{CNTI} $\cdotp$}{Venezuela.}

\Description{\MarginDate{GNU/Linux Development}Integration of many FLOSS technologies into the Operative System and platform to be used by all the Venezuelan Public Administration (Canaima GNU/Linux). This became an important basement for all social and tecnological proyects such as -Canaima Educativo- wich gives a laptop per child, filled with open source software intended for education. Funded by the National Information Technologies Center (\href{http://cnti.gob.ve/}{CNTI}) all open source and comunity oriented. Debian based. (Python, Bash, pyGTK, Django, Xen)}  
\Description{\textit{\textbf{3D Blender Animation}}\ \ $\cdotp$\ \ \MarginDate{Teaching} Basic Intensive Course $\cdotp$ 3D presentations $\cdotp$ Duration: 1 Week $\cdotp$ \textbf{FLOSS Academy} }
\Description{\textit{\textbf{Blender Advanced}}\ \ $\cdotp$\ \ \MarginDate{} Intensive Advanced Course$\cdotp$ Postprod and edition $\cdotp$ Duration: 1 Week $\cdotp$ \textbf{FLOSS Academy} }
\Description{\textit{\textbf{Python Basic}}\ \ $\cdotp$\ \ \MarginDate{} Python basic programming $\cdotp$ General introduction, plus version control system (git) $\cdotp$ Duration: 3 days $\cdotp$ \textbf{FLOSS Academy} }

\Sep

\NewWorkExperience{2007--2008}{\textbf{Huawei Technologies} $\cdotp$}{Venezuela.}

\Description{\MarginDate{Internship \& Engineering Design}6-month internship, and former Engineer in EDD (Engineering Design Department) for the deployment of Huawei UMTS technologies for local telecom provider: Movilnet.}
\vspace{1.5em}

\spacedlowsmallcaps{Formal Education}
\vspace{0.5em}

\NewWorkExperience{2013}{\textbf{MongoDB University} $\cdotp$}{Online}
\Description{\newline \textit{\textbf{M101P: MongoDB for Developers (Python)}}\ \ $\cdotp$\ \  Topics: \MarginDate{MongoDB}Everything needed to know for building MongoDB-based apps}
\vspace{0.5em}

\NewWorkExperience{2012}{\textbf{CLEAR CORP.} $\cdotp$}{Costa Rica}
\Description{\newline \textit{\textbf{OpenERP Technical Trainning}}\ \ $\cdotp$\ \  Topics: \MarginDate{OpenERP Open Business Solutions}OpenERP Modules Development.}
\vspace{0.5em}

\NewWorkExperience{2011}{\textbf{FLOSS Academy} $\cdotp$}{Caracas, VE}
\Description{\newline \textit{\textbf{Python Advanced I}}\  \  Topics: \MarginDate{Python}Virtualenv\ $\cdotp$\ version control systems\ $\cdotp$\ Documentation\ $\cdotp$\ reStructured formatting\ $\cdotp$\ Web Frameworks\ $\cdotp$\ Django\ $\cdotp$\ Databases\ $\cdotp$\ GUI libs\ $\cdotp$\ Iterators\ $\cdotp$\ Generators\ $\cdotp$\ Decorators\ $\cdotp$\ Unittest.}
\vspace{0.5em}
\NewWorkExperience{2010}{\textbf{FLOSS Academy} $\cdotp$}{Caracas, VE}

\Description{\textit{\textbf{Platform Services Kit}}\  \  Topics: \MarginDate{SysAdmin}Xen\ $\cdotp$\ OpenLDAP\ $\cdotp$\ PAM\ $\cdotp$\ OpenVPN\ $\cdotp$\ Postfix\ $\cdotp$\ NTP\ $\cdotp$\ DNS\ $\cdotp$\ Apache\ $\cdotp$\ Vhosts\ $\cdotp$\ Samba\ $\cdotp$\ DHCP. }
\vspace{0.5em}

\NewWorkExperience{2010}{\textbf{FLOSS Academy} $\cdotp$}{Caracas, VE}

\Description{\textit{\textbf{CCNA}}\ \ \  Topics: \MarginDate{Network Admin}Medium sized routed and switched networks\ $\cdotp$\ WAN\ $\cdotp$\ IP\ $\cdotp$\ EIGRP\ $\cdotp$\ Frame Relay\ $\cdotp$\ RIPv2\ $\cdotp$\ VLANs\ $\cdotp$\ Ethernet\ $\cdotp$ and access control lists.}

\vspace{0.5em}
\vspace{0.5em}
\NewWorkExperience{2007}{\textbf{Universidad del Táchira} $\cdotp$}{San Cristóbal, VE}

\Description{\textit{\textbf{Electronic Engineer}}\  \  Major: Processes automation\MarginDate{Engineering} Strong Knowelledge in Math, Physics, Chemistry, Language. $\cdotp$ Logic and abstract thinking $\cdotp$ Informatics integration}

\vspace{1.5em}

\spacedlowsmallcaps{Additional Information}
\vspace{0.5em}


\Description{\textsc{Event:} \MarginDate{FLOSS Activist and Evangelist} FLOSS Congress \textit{Táchira} $\cdotp$\ \ (2011) \ Ponent: Canaima GNU/Linux}
\Description{\textsc{Event:} FLISOL \textit{San Cristóbal} $\cdotp$\ \ (2010) \ Ponent: Canaima GNU/Linux}
\Description{\textsc{Event:} FLOSS Congress \textit{Táchira} $\cdotp$\ \ (2010) \ Ponent: Canaima GNU/Linux}
\Description{\textsc{Event:} FLISOL \textit{San Cristóbal} $\cdotp$\ \ (2009) \ Ponent: Canaima GNU/Linux}
\Description{\textsc{Event:} FLOSS Congress \textit{Caracas} $\cdotp$\ \ (2008) \ Ponent: GNU/Linux Development}
\Description{Since 2008$\cdotp$ Former \textit{Canaima GNU/Linux} Developer}
\Description{\textsc{Event:} FLISOL \textit{San Cristóbal} $\cdotp$\ \ (2006) \ Organizer Comitee}
\Description{\textsc{Event:} FLISOL \textit{San Cristóbal} $\cdotp$\ \ (2005) \ Organizer Comitee}
\Description{Since 2003 $\cdotp$ Member of Local Linux User Group (TALUG)}

\vspace{1em}

\newlength{\langbox}
\settowidth{\langbox}{English.}

\Description{\parbox{\langbox}{\textsc{English}}\ \ $\cdotp$\ \  \ Fluent $\cdotp$ Written and spoken.}
\MarginDate{Languages}
\vspace{0.5em}

\Description{\parbox{\langbox}{\textsc{Spanish}}\ \ $\cdotp$\ \ \  Mother Language}
\vspace{1em}

\Description{\LaTeX\ \MarginDate{Interests}\  $\cdotp$\ FLOSS $\cdotp$\ Open Culture $\cdotp$\ Typography\ $\cdotp$\ Programming\ $\cdotp$\ Graphic Design\ $\cdotp$\ Animation \ $\cdotp$\ Web Development and Design \ $\cdotp$\ Open Source Hardware \ $\cdotp$\ Raspberry \ $\cdotp$\ 3D Design \& Animation \ $\cdotp$ \ Blender  \ $\cdotp$ \ Arts  \ $\cdotp$ \ Data Representation\ $\cdotp$ Photography \ $\cdotp$ \ High Functionality and Performance Programming }
\enlargethispage{\baselineskip}
\end{cv}
\end{document}
